Structured Versus Decorated Cospans

### 2020-12-30 cospans.tex
Changed proof of Lemma 4.1; explained decoration morphism tau_f there

We show that any vertical 1-morphism $f \maps a \to b'$ in $F\lCsp$ has a companion and a conjoint.  This horizontal 1-cell $\hat{f}$:

@@

 a\xrightarrow{f}b\xleftarrow{1}b,\quad \bot_{b} \in F(b)

@@

where $\bot_b$ is the trivial decoration as in \cref{eq:UFCsp}, is a companion of $f$ because the following two 2-morphisms, having $\hat{f}$ as
source and target:

@@

{\chris The decoration morphisms should be both isomorphisms due to pseudofunctoriality of F...}
satisfy the equations required of a companion \cref{eq:CompanionEq}, using vertical \cref{eq:verticalcompo} and horizontal \cref{eq:horizontalcompo} composition of 2-cells in this double category:

@@

and right hand sides of the above two equations are given respectively by the 2-morphisms $U_f$ and $1_{\hat{f}}$. The conjoint of $f$ is given by this horizontal 1-cell $\check{f}$, which is just the opposite of the companion above:

>>>>

We show that any vertical 1-morphism $f \maps a \to b'$ in $F\lCsp$ has a companion and a conjoint.  First, we can make ths horizontal 1-cell $\hat{f}$:

@@

 a\xrightarrow{\;f\;}b\xleftarrow{\;1\;}b,\quad \bot_{b} \in F(b)

@@

where $\bot_b$ is the trivial decoration as in \cref{eq:UFCsp}, into a companion of $f$ using the following 2-morphisms:

@@

where the decoration morphism $\tau_f$ is the isomorphism given by the pseudofunctoriality of $F$:
\node (A) at (0,0) {$\one$};
\node (B) at (1,0) {$F(0)$};
\node (C) at (2.2,0.5) {$F(a)$};
\node (C') at (2.2,-0.5) {$F(b)$};
\node (D) at (1.8,0) {{\rotatebox{90}{$\cong$}}$\Downarrow$};
(A) edge node[above]{$\phi_0$} (B)
(B) edge node[above]{$F(!_a)\;$} (C)
(B) edge node[below]{$F(!_b)\;\;$} (C')
(C) edge node[right]{$F(f)$} (C');
These 2-morphisms satisfy equations required of a companion \cref{eq:CompanionEq}, using vertical \cref{eq:verticalcompo} and horizontal \cref{eq:horizontalcompo} composition of 2-cells in this double category:

@@

since the right hand sides of the above two equations are given respectively by the 2-morphisms $U_f$ and $1_{\hat{f}}$. The conjoint of $f$ is given by this horizontal 1-cell $\check{f}$, which is just the opposite of the companion above:
